Impact of Exam Format on Student Learning Outcomes

### 2019-10-19 CUT/paper.tex
fixing abstract

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\doublespace
\title{Impact of Exam Format on Student Learning Outcomes}
\author{W. Justin Toth\\Combinatorics and Optimization\\20411831}
\begin{document}
\maketitle
\begin{abstract}
We study of question of how exam formats impact student study behaviours, learning outcomes, and perception of the courses they take. We particularly focus on Mathematics and Science courses, but the findings in this survey are general enough to be widely applicable. We study multiple choice versus constructed response, how much reference material to allow in the exam room, oral versus written exams, and the Two Stage method for injecting collaborative learning into exams.
\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}

>>>>

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\doublespace
\title{Impact of Exam Format on Student Learning Outcomes}
\author{W. Justin Toth\\Combinatorics and Optimization\\20411831}
\begin{document}
\maketitle
\begin{abstract}
We study the question of how exam formats impact student study behaviours, learning outcomes, and perception of the courses they take. We particularly focus on Mathematics and Science courses, but the findings in this survey are general enough to be widely applicable. We study multiple choice versus constructed response, how much reference material to allow in the exam room, oral versus written exams, and the Two Stage method for injecting collaborative learning into exams.
\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}
